A publishing infrastructure for AI-assisted academic authoring

### 2023-12-20 latex/manuscript.tex
latex: minor fixes in manuscript.tex

\textbf{Objective:} In this work, we investigate the use of advanced natural language processing models to reduce the time-consuming process of writing and revising scholarly manuscripts.\\
\textbf{Materials and Methods:} For this purpose, we integrate large language models into the Manubot publishing ecosystem to suggest revisions for scholarly texts.
Our AI-based revision workflow employs a prompt generator that incorporates manuscript metadata into templates, generating section-specific instructions for the language model.
The model then generates revised versions of each paragraph for human authors to review.
We evaluated this methodology through three case studies of existing manuscripts, including the revision of this manuscript.\\
\textbf{Results:} Our results indicate that these models, despite some limitations, can grasp complex academic concepts and enhance text quality.
All changes to the manuscript are tracked using a version control system, ensuring transparency in distinguishing between human- and machine-generated text.\\
\textbf{Conclusions:} Given the significant time researchers invest in crafting prose, incorporating large language models into the scholarly writing process can significantly improve the type of knowledge work performed by academics.
Our approach also enables scholars to concentrate on critical aspects of their work, like the novelty of their ideas, while automating tedious tasks such as adhering to specific writing styles.
Although the use of AI-assisted tools in scientific authoring is controversial, our approach, which focuses on revising human-written text and provides change-tracking transparency, can mitigate concerns regarding AI's role in scientific writing.

@@

>>>>

\textbf{Objective:} Investigate the use of advanced natural language processing models to reduce the time-consuming process of writing and revising scholarly manuscripts.\\
\textbf{Materials and Methods:} For this purpose, we integrate large language models into the Manubot publishing ecosystem to suggest revisions for scholarly texts.
Our AI-based revision workflow employs a prompt generator that incorporates manuscript metadata into templates, generating section-specific instructions for the language model.
The model then generates revised versions of each paragraph for human authors to review.
We evaluated this methodology through three case studies of existing manuscripts, including the revision of this manuscript.\\
\textbf{Results:} Our results indicate that these models, despite some limitations, can grasp complex academic concepts and enhance text quality.
All changes to the manuscript are tracked using a version control system, ensuring transparency in distinguishing between human- and machine-generated text.\\
\textbf{Conclusions:} Given the significant time researchers invest in crafting prose, incorporating large language models into the scholarly writing process can significantly improve the type of knowledge work performed by academics.
Our approach also enables scholars to concentrate on critical aspects of their work, like the novelty of their ideas, while automating tedious tasks such as adhering to specific writing styles.
Although the use of AI-assisted tools in scientific authoring is controversial, our approach, which focuses on revising human-written text and provides change-tracking transparency, can mitigate concerns regarding AI's role in scientific writing.

@@

\hypertarget{conclusions}{%
\subsection{Conclusions}\label{conclusions}}
